%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Hyperlinks
\usepackage{hyperref}

% Set applicant's personal data for header
\name{Ibrahim I. Jarif}
\address{101 Animish Apartment\linebreak Deopur, Dhule - 424002\linebreak Maharashtra, India}
\contacts{(+91) 904-942-6428 \linebreak jarifibrahim@gmail.com \linebreak github.com/jarifibrahim}

\begin{document}

	% Print the header
	\makeheader

	\begin{cvsection}{Education}
		\begin{cvsubsection}{Dhule, Maharashtra, India}{North Maharashtra University}{}
			\begin{itemize}
				\item Bachelor of Engineering (B.E.) -- Computer Engineering from S.S.V.P.S's Bapusaheb Shivajirao Deore College of Engineering, Dhule. CGPA: 8.43/10 (Current) \hfill May 2017 (Expected)
				\item Higher Secondary Education -- Jai Hind Junior College, Dhule. 75.83\%. \hfill February 2013
				\item Secondary Education -- Canossa Convent High School, Dhule. 87.83\%.\hfill March 2011
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	% Print the content
	\begin{cvsection}{Open Source Contribution}
		\begin{cvsubsection}[2]{Student Developer\linebreak Google Summer of Code}{The Apache Software Foundation}{April 2016 -- August 2016}
			Smoke Tests and Continuous Integration Infrastructure for Apache Open Climate Workbench
			\begin{itemize}
				\item Added unit tests and improved the test coverage from 59\% to 80\%.
				\item Configured Continuous Integration builds on Travis CI (Build + tests), coveralls.io (tests coverage) and landscape.io (code quality).
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}[2]{Committer and Project Management Committee Member}{The Apache Software Foundation}{March 2016 -- Present}
			\begin{itemize}
				\item Contributing features, improvements and bug fixes to Apache Open Climate Workbench.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	\begin{cvsection}{Voluntary Work}
		\begin{cvsubsection}{Programming Volunteer}{Ashoka Globalizer}{July 2016 -- September 2016}
			\begin{itemize}
				\item Designed and implemented a dashboard template in Google Spreadsheets which will be used to keep track of team issues and status.
				\item Added features like automatic reminder emails, welcome emails, team status indicators, automatically generated and updated Google forms.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Knowledge}{}{}
	All the Projects listed below are available at     \textbf{\url{https://github.com/jarifibrahim}}   \\     \begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
			    
			    \item \textbf{Ashoka-Dashboard} (\url{https://github.com/jarifibrahim/ashoka-dashboard}) -- A Team Status Management Dashboard built using Django Web Framework. Features - Automated reminder emails, Survey Forms, Team Health indicators, etc.
			    
				\item \textbf{Yet Another Sessionization Tool (YAST)}
				(\url{https://github.com/jarifibrahim/YAST}) -- YAST can be used perform sessionization on web/proxy server log files. The tool generates sessionized data (which includes- Total sessions, List of URLs) that can be used for web usages analysis. The tool is a parser that cleans log file according to user configuration.
				
	    		\item \textbf{ResultBot}                (\url{https://github.com/jarifibrahim/resultBot}) -- A python script to download North Maharashtra University results and email it to a list of recipients. 
			    
			    \item \textbf{Fynance} (\url{https://fynance.herokuapp.com})
			        -- A web application to buy and sell stocks (real stocks, fake shares). The web app is built using the flask (Python Framework) and uses MongoDB as the database.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Awards}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Runner Up at IET's Present Around The World -- Mumbai Local Network Level and North Maharashtra University Level} -- Gave a presentation on Django (Python web framework).
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Skills and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Python; Django; C; HTML; CSS; BootStrap; Git; Linux
				\item  JavaScript; JQuery; Flask; Nose (Testing Framework); Google App Scripts; Travis CI
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
